Selecting Team Members of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Based on Performance and Stability To Maximize Success

### 2024-01-15 manuscript/submission.tex
reorganizing numbered method list

\begin{enumerate}
  \item Determine the best individual apparatus candidates.
  \begin{enumerate}
    \item Calculate and examine the mean and standard deviations of each American female athlete's score 
    on each apparatus.
    \item Calculate the number of observations for each athlete on each apparatus.
    \item Plot the mean versus the standard deviation of the ten athletes with the highest mean scores on each 
    apparatus.
    \begin{enumerate}
      \item Use these plots as a visual to represent the possible scores that could be achielved in each apparatus 
     component of the Olympics.
     \item Using the plots, create a parameter for each apparatus that uses both mean score and standard 
     deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
     States on each apparatus.
     \begin{enumerate}
       \item Select the five athletes with the highest parameter value for each apparatus to identify the ``best'' 
        five athletes that compete on each apparatus based on both their success, a high mean score, and their 
        inconsistency, their standard deviation.
     \end{enumerate}
     \item Identify the athletes with the two largest paramter values as the ``best'' on each apparatus.
    \end{enumerate}
  \end{enumerate}
  \item Determine the best individual all-around candidates.
  \begin enumerate
   \item Produce a list of ``target athletes'' for furture computations that contains all athletes that were identified 
   as being in the top five for any apparatus in the last step.
   \begin{enumerate}
     \item Remove any athletes from the ``target athletes'' list that have not competed on all aparatuses.
   \end{enumerate}
   \item Calculate the sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
    \item Plot the mean score sum versus the standard deviation sum for each ``target athlete.''
   \begin{enumerate}
     \item Use this plot as a visual to represent the possible scores that could be achielved in the individual all-around 
     component of the Olympics.
   \end{enumerate}
  \end{enumerate}
  \item Determine the best team all-around candidates.
  \begin{enumerate}
   \item Calculate the summed mean score and standard deviation sum of every combination of three athletes using the previously 
   calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
   \item Plot the summed mean score versus the standard deviation for the ten combinations of three athletes with the 
   highest summed mean score.
   \begin{enumerate}
     \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team finals 
    component of the Olympics.
   \end{enumerate}
   \item Calculate the summed mean score and standard deviation sum of every combination of four athletes using the previously 
   calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
   \item Plot the summed mean score versus the standard deviation for the ten combinations of four athletes with the 
   highest summed mean score.
   \begin{enumerate}
      \item Use this plot as a visual to represent the possible scores that could be achielved in the all-around team qualifying  
     round of the Olympics.
   \end{enumerate}
  \end{enumerate}
\item Visully exammine each produced plot to build a final team of five in an effort to include in 
    the final team the best three candidates for the team all-around, the best candidate for the fourth qualifying position, 
    the best two candidates for the individual all-around, and the two athletes that are superior on each apparatus.
\end{enumerate}

>>>>

\begin{enumerate}
  \item Determine the best individual apparatus candidates.
  \begin{enumerate}
    \item Calculate and examine the mean and standard deviations of each American female athlete's score 
    on each apparatus.
    \item Calculate the number of observations for each athlete on each apparatus.
    \item Plot the mean versus the standard deviation of the ten athletes with the highest mean scores on each 
    apparatus.
    \begin{enumerate}
      \item Use these plots as a visual to represent the possible scores that could be achieved in each apparatus 
     component of the Olympics.
     \item Using the plots, create a parameter for each apparatus that uses both mean score and standard 
     deviation to identify which athletes are best suited to be considered to compete on behalf of the United 
     States on each apparatus.
     \begin{enumerate}
       \item Select the five athletes with the highest parameter value for each apparatus to identify the ``best'' 
        five athletes that compete on each apparatus based on both their success, a high mean score, and their 
        inconsistency, their standard deviation.
     \end{enumerate}
     \item Identify the athletes with the two largest parameter values as the ``best'' on each apparatus.
    \end{enumerate}
  \end{enumerate}
  \item Determine the best individual all-around candidates.
  \begin{enumerate}
   \item Produce a list of ``target athletes'' for future computations that contains all athletes that were identified 
   as being in the top five for any apparatus in the last step.
   \begin{enumerate}
     \item Remove any athletes from the ``target athletes'' list that have not competed on all apparatuses.
   \end{enumerate}
   \item Calculate the sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
    \item Plot the mean score sum versus the standard deviation sum for each ``target athlete.''
   \begin{enumerate}
     \item Use this plot as a visual to represent the possible scores that could be achieved in the individual all-around 
     component of the Olympics.
   \end{enumerate}
  \end{enumerate}

\item Determine the best team all-around candidates.
  \begin{enumerate}
   \item Calculate the summed mean score and standard deviation sum of every combination of three athletes using the previously 
   calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
   \item Plot the summed mean score versus the standard deviation for the ten combinations of three athletes with the 
   highest summed mean score.
   \begin{enumerate}
     \item Use this plot as a visual to represent the possible scores that could be achieved in the all-around team finals 
    component of the Olympics.
   \end{enumerate}
   \item Calculate the summed mean score and standard deviation sum of every combination of four athletes using the previously 
   calculated sum of each ``target athlete's'' mean score for each apparatus and the sum of each athlete's standard 
   deviation for each apparatus.
   \item Plot the summed mean score versus the standard deviation for the ten combinations of four athletes with the 
   highest summed mean score.
   \begin{enumerate}
      \item Use this plot as a visual to represent the possible scores that could be achieved in the all-around team qualifying  
     round of the Olympics.
   \end{enumerate}
  \end{enumerate}

\item Visually examine each produced plot to build a final team of five in an effort to include in 
    the final team the best three candidates for the team all-around, the best candidate for the fourth qualifying position, 
    the best two candidates for the individual all-around, and the two athletes that are superior on each apparatus.
\end{enumerate}
